Notes on RBFs methods for Neural Fields

### 2023-11-14 Manuscript/manuscript.tex
Added section on projection methods

\section{Example of collocation scheme for a neural field on a ring} 
Let us consider a neural field model on a ring, with cosine synaptic kernel, 
\begin{equation}\label{eq:NFRing}
  \begin{aligned}
 & \partial_t u(x,t) =  -u(x,t) + g(x,t)+ \int_{-\pi}^{\pi} \cos(|x-x'|) f(u(x',t)) dx',
   \qquad x \in [-\pi,\pi) \\
 & u(x,0) = v(x) 
  \end{aligned}
\end{equation}
where $g$, $f$, and $v$ are prescribed functions, and let us derive an intuitive scheme
for this problem. We pick $n+1$ evenly spaced points in $[-\pi,\pi]$
\begin{equation}\label{eq:nodesRing}
  x_i = -\pi + h i, \qquad h = \frac{2\pi}{n}, \qquad i = 0, \ldots, n.
\end{equation}
Because of periodicity, we expect to need only $n$ of those $n+1$ points, and indeed
this turns out to be the case. If $v(x)$ is a periodic function, applying the
trapezium rule with the grid above gives (note the sum runs over just $n$ points)
\[
  \int_{-\pi}^{\pi} v(x')\,d x' \approx \sum_{j=1}^{n} v(x_j) h.
\]
The integrand in \cref{eq:NFRing} is periodic in $x'$, so we evaluate the neural
field at $x_1, \ldots, x_n$ ($x_0$ excluded) and simultaneously apply the quadrature rule
above to obtain
\[
  \begin{aligned}
  & U'_i(t) = -U_i(t) + \sum_{j=1}^{n} \cos(x_i - x_j) f(U_j(t)) h + G_i(t), \qquad i = 1,\ldots,n  \\
  & U_i(0) = V_i
  \end{aligned}
\]
that is, a system in the form 
\begin{equation}\label{eq:NFODE}
  \begin{aligned}
   &  U'(t) = - U(t) + M F(U(t)) +  G(t)\\ 
   &  U(0) = V
  \end{aligned}
\end{equation}  
in which $U(t), G(t), F(U(t)), V$ are vectors in $\RSet^n$ for all $t$, and in which
$M$ is the $n$-by-$n$, full matrix entries $M_{ij} = \cos(x_i - x_j)h$. The intention
here is to use $U_i(t)$ as an approximation for $u(x_i,t)$.

@@

In \cite{avitabileProjectionMethodsNeural2023} it is shown that the scheme discussed
above stems from the following choices: 
\begin{enumerate}
  \item The points are evenly spaced in $[-\pi,\pi]$.
  \item The function $v_n$ that subtends the scheme is of the following form:
    \begin{equation}\label{eq:LagrangeInterp}
      v_n(x) = \sum_{j=1}^{n} v(x_j) \ell_j(x), 
    \end{equation}
    where $\ell_i(x)$ are Lagrange polynomials, hence $\ell_i(x_j) = \delta_{ij}$.
    This choice of $v_n$ is one way to solve the interpolation
    \cref{prob:interpolation}.
\end{enumerate}
In \cite{avitabileProjectionMethodsNeural2023} it is also shown that a variety of
other schemes, of Finite Elements or Galerkin type, are analysable following a common
framework.

@@

  Using RBFs is promising and interesting because of the following points:
  \begin{itemize}
      \item RBF handle point distributions in a flexible and adaptable manner. They
        work well in multiple spatial dimensions, and on curved geometries. It is is
        relatively simple to add points where it is needed; RBFs are constructed
        using translates of a kernel function, without a mesh.
      \item Convergence results for RBFs seem available in literature, so there is
        hope to connect to the framework in
        \cite{avitabileProjectionMethodsNeural2023} and quickly obtain convergence
        rates.
      \item We will focus on RBF interpolants of the form
        \begin{equation}\label{eq:RBFInterpolation}
          v_n(x) = \sum_{i=1}^{n} \sum_{j=1}^{k_i} V_{ij} \Phi(\| x - \xi_{ij} \|),
        \end{equation}
        where $\xi_{ij}$ are suitably chosen subsets of $\{ x_i \}$, as we will
        specify later. This form of interpolation induces a \textit{sparsification}
        of the matrix $M$.
  \end{itemize}

@@

@@

Let us consider a neural field posed on
a compact domain $D \subset \RSet^d$
\begin{equation}\label{eq:NF}
  \begin{aligned}
  &
  \begin{aligned}
    \partial_t u(x,t) =  -u(x,t)  &+ g(x,t) \\
                & + \int_{D} w(x,x') f(u(x',t))d \mu(x'),
  \end{aligned}
  && (x,t) \in D \times [0,T] \\
  & u(x,0) = v(x) && x \in D 
  \end{aligned}
\end{equation}
It is assumed here that the integral is on a manifold, hence it is expressed in terms
of a measure $\mu$. Heuristically, a collocation scheme for \cref{eq:NF} can be conceived
in steps, as follows:

\textbf{Step 1: nodes selection.} Pick $n$ points in the domain $D$. We denote them by
$\Xi = \{ x_i \}_{i \in \NSet_n} \subset D$. \da[]{I have used $\NSet_n = \{ 1,\ldots,n
\}$. I also dislike $\Xi$, we can change it later} In what follows, it may be useful to make $n$ depend on a positive real number
$h$, a discretisation parameter, so that $n(h) \to \infty$ as $h \to 0$, or as $h \to
\infty$. An example of such relationship is given in \cref{eq:nodesRing}. We will
omit the dependence of $n$ on $h$ when possible.

\textbf{Step 2: Collocation.} 
Impose that \cref{eq:NF} holds at each node (\textit{collocate the equation} at
each $x_i \in \Xi$). This means replacing \cref{eq:NF} by a set of $n$ equations
\begin{equation}\label{eq:NFColl}
  \begin{aligned}
  &
  \begin{aligned}
    \partial_t u_n(x_i,t) =  -u_n(x_i,t) &+ g(x_i,t) \\
                & + \int_{D} w(x_i,x') f(u_n(x',t))d \mu(x'),
  \end{aligned}
  && (x_i,t) \in \Xi \times [0,T] \\
  & u_n(x_i,0) = v(x_i) && x_i \in \Xi 
  \end{aligned}
\end{equation}

@@

\textbf{Step 3: Quadrature.} Select a quadrature for the integral, and solve
\begin{equation}%\label{eq:NFODE}
  \begin{aligned}
   & \tilde U'(t) = -\tilde U(t) + K(\tilde U(t)) + \tilde G(t) \qquad  t \in [0,T]\\ 
   & \tilde U(0) = V
  \end{aligned}
\end{equation}  
where $\tilde U(t), G(t), K(\tilde U(t)) \in \RSet^n$ for all $t$, and $\tilde U_i(t)$ approximates
$u_n(x_i,t)$. The nonlinear mapping $K(U)$ involves a matrix-vector multiplication,
and incorporates quadrature weights.

\section{Collocation schemes as interpolatory projection schemes}\label{sec:projectionSchemes} 
\da[inline]{This section can be skipped at a first pass}

Once we have refined the steps of a collocation scheme, we can bring interpolation
into the picture. In \cite{avitabileProjectionMethodsNeural2023} it is shown that convergence estimates
for the collocation scheme (and other schemes) are possible disregarding step 3. In
fact, with just steps 1-2 can estimate how fast $u_n$ tends to $u$, as $n \to \infty$.
Once a convergence rate is established, then this instructs which quadrature scheme
to select: the quadrature should respects this rate, so that we can use $\tilde U_i$ as an
approximation to $u(x_i,t)$, not simply $u_n(x_i,t)$.

We do not have to get into the details of
\cite{avitabileProjectionMethodsNeural2023}, but one aspect is important for these
notes: it is useful to understand how \cref{eq:NFColl} is derived from \cref{eq:NF}
using a projection. The RBFs will provide, in fact, a flexible and accurate
\textit{interpolatory projector}.

To make progress on this, let us assume we seek for a solution to the neural field
equations in the space of continuous functions $\XSet = C(D)$. A projector $P_n$ is a
linear mapping from $\XSet$ to an $n$-dimensional subspace $\XSet_n \subset \XSet$
such that $P_n (P_n v) = P_n v$ for all $v \in \XSet$. The distinctive feature of an
\textit{interpolatory projector} is that it has the property  
\[
  (P_n v)(x_i) = v(x_i), \qquad x_i \in \Xi,
\] 
that is, $P_n v$ is a function of $x$, which approximates $v(x)$, and it is exact
at the nodes $x_i$. The previous sections contain two interpolatory projectors in
disguise. In \cref{eq:LagrangeInterp} we wrote
\[
  v_n(x) = \sum_{j=1}^{n} v(x_j) \ell_j(x). 
\]
Now $v$ is a continuous function so $v \in \XSet$, and $v_n$ is a linear combination
of $\{ \ell_j \}_{j=1}^n$, so $v_n \in \XSet_n = \spn \{ \ell_1, \ldots, \ell_n \}$.
This means we can interpret the previous writing as
\[
  (P_n v)(x) = \sum_{j=1}^{n} v(x_j) \ell_j(x),
\]
that is, $v_n$ is the action of $P_n$ on the function $v$, $v_n = P_n v$.
The same can be said about \cref{eq:RBFInterpolation}, which defines another choice
of the interpolant. Another choice of projector $P_n$.

Writing things in terms of $P_n$ is useful, as it compactifies the notation. Firstly,
it is possible to rewrite the neural field equation \cref{eq:NF} as the following
Cauchy problem on the Banach space $\XSet$
\begin{equation}\label{eq:cauchy}
  \begin{aligned}
  & \dot U(t) = - U(t) + WF(U(t)sketch.pnsketch.pngg) + G(t) =:  N(U(t),t), \qquad t \in J, \\
  & U(0) = V.
  \end{aligned}
\end{equation}
The identification with \cref{eq:NF} is established with the positions
\[
  \begin{aligned}
   & V = v(\blank)\\
   & U \colon [0,T] \to \XSet, && t \mapsto u(\blank,t) \\
   & G \colon [0,T] \to \XSet, && t \mapsto g(\blank,t) \\
   & W \colon \XSet \to \XSet, && v \mapsto \int_{D} w(\blank,y) v(y) \,d \mu(x') \\
   & F \colon \XSet \to \XSet, && v \mapsto f(v). 
  \end{aligned}
\]
The Cauchy problem is well-posed under general assumptions that is, there is a unique
$u \in C^1(J,\XSet)$ satisfying \cref{eq:cauchy}.

Secondly, it is possible to interpret \cref{eq:NFColl} in operator form, as
\begin{equation}\label{eq:cauchyPn}
  \begin{aligned}
  & \dot U_n(t) = - U_n(t) + P_n WF(U(t)) + P_n G(t) =  P_n N(U_n(t),t), \qquad t \in J, \\
  & U_n(0) = P_n V,
  \end{aligned}
\end{equation}
which is a Cauchy problem on the space $\XSet_{n}$.

@@

\subsection{References} \label{sec:references}
These are random citations \cite{KoMa14,siam}. For cross-references I use
\texttt{cleveref}: like this
\cref{eq:test}, like this \Cref{eq:test}, or like this \cref{sec:conventions}, or
this \cref{hyp:trivial}, or this \cref{clm:trivial}.
\begin{equation}\label{eq:test}
  x = y
\end{equation}

>>>>

\section{Example of collocation scheme for a neural field on a ring} 
Let us consider a neural field model on a ring, with cosine synaptic kernel, 
\begin{equation}\label{eq:NFRing}
  \begin{aligned}
 & \partial_t u(x,t) =  -u(x,t) + g(x,t)+ \int_{-\pi}^{\pi} \cos(|x-y|) f(u(y,t)) dy,
   \qquad x \in [-\pi,\pi) \\
 & u(x,0) = v(x) 
  \end{aligned}
\end{equation}
where $g$, $f$, and $v$ are prescribed functions, and let us derive an intuitive scheme
for this problem. We pick $n+1$ evenly spaced points in $[-\pi,\pi]$
\begin{equation}\label{eq:nodesRing}
  x_i = -\pi + h i, \qquad h = \frac{2\pi}{n}, \qquad i = 0, \ldots, n.
\end{equation}
Because of periodicity, we expect to need only $n$ of those $n+1$ points, and indeed
this turns out to be the case. If $v(x)$ is a periodic function, applying the
trapezium rule with the grid above gives (note the sum runs over just $n$ points)
\[
  \int_{-\pi}^{\pi} v(y)\,d y \approx \sum_{j=1}^{n} v(x_j) h.
\]
The integrand in \cref{eq:NFRing} is periodic in $y$, so we evaluate the neural
field at $x_1, \ldots, x_n$ ($x_0$ excluded) and simultaneously apply the quadrature rule
above to obtain
\[
  \begin{aligned}
  & U'_i(t) = -U_i(t) + \sum_{j=1}^{n} \cos(x_i - x_j) f(U_j(t)) h + G_i(t), \qquad i = 1,\ldots,n  \\
  & U_i(0) = V_i
  \end{aligned}
\]
that is, a system in the form 
\begin{equation}
  \begin{aligned}
   &  U'(t) = - U(t) + M F(U(t)) +  G(t)\\ 
   &  U(0) = V
  \end{aligned}
\end{equation}  
in which $U(t), G(t), F(U(t)), V$ are vectors in $\RSet^n$ for all $t$, and in which
$M$ is the $n$-by-$n$, full matrix entries $M_{ij} = \cos(x_i - x_j)h$. The intention
here is to use $U_i(t)$ as an approximation for $u(x_i,t)$.

@@

In \cite{Avitabile:2023ab} it is shown that the scheme discussed
above stems from the following choices: 
\begin{enumerate}
  \item The points are evenly spaced in $[-\pi,\pi]$.
  \item The function $v_n$ that subtends the scheme is of the following form:
    \begin{equation}\label{eq:LagrangeInterp}
      v_n(x) = \sum_{j=1}^{n} v(x_j) \ell_j(x), 
    \end{equation}
    where $\ell_i(x)$ are Lagrange polynomials, hence $\ell_i(x_j) = \delta_{ij}$.
    This choice of $v_n$ is one way to solve the interpolation
    \cref{prob:interpolation}.
\end{enumerate}
In \cite{Avitabile:2023ab} it is also shown that a variety of
other schemes, of Finite Elements or Galerkin type, are analysable following a common
framework.

@@

  Using RBFs is promising and interesting because of the following points:
  \begin{itemize}
      \item RBF handle point distributions in a flexible and adaptable manner. They
        work well in multiple spatial dimensions, and on curved geometries. It is is
        relatively simple to add points where it is needed; RBFs are constructed
        using translates of a kernel function, without a mesh.
      \item Convergence results for RBFs seem available in literature, so there is
        hope to connect to the framework in
        \cite {Avitabile:2023ab} and quickly obtain convergence
        rates.
      \item We will focus on RBF interpolants of the form
        \begin{equation}\label{eq:RBFInterpolation}
          v_n(x) = \sum_{i=1}^{n} \sum_{j=1}^{k_i} V_{ij} \Phi(\| x - \xi_{ij} \|),
        \end{equation}
        where $\xi_{ij}$ are suitably chosen subsets of $\{ x_i \}$, as we will
        specify later. This form of interpolation induces a \textit{sparsification}
        of the matrix $M$.
  \end{itemize}

@@

\section{Notation}\label{sec:notation} We will use the index sets by $\NSet_n = \{
1,\ldots, n\}$. In addition, we will endow $\RSet^n$ with the standard Euclidean
norm, which we shall denote by $\|\blank\|_2$, or simply $\| \blank \|$.

@@

Let us consider a neural field posed on
a compact domain $D \subset \RSet^d$
\begin{equation}\label{eq:NF}
  \begin{aligned}
  &
  \begin{aligned}
    \partial_t u(x,t) =  -u(x,t)  &+ g(x,t) \\
                & + \int_{D} w(x,y) f(u(y,t))d \mu(y),
  \end{aligned}
  && (x,t) \in D \times [0,T] \\
  & u(x,0) = v(x) && x \in D 
  \end{aligned}
\end{equation}
It is assumed here that the integral is on a manifold, hence it is expressed in terms
of a measure $\mu$. Heuristically, a collocation scheme for \cref{eq:NF} can be conceived
in steps, as follows:

\textbf{Step 1: nodes selection.} Pick $n$ points in the domain $D$. We denote them by
$\Xi = \{ x_i \}_{i \in \NSet_n} \subset D$. In what follows, it may be useful to
make $n$ depend on a positive real number $h$, a discretisation parameter, so that
$n(h) \to \infty$ as $h \to 0$, or as $h \to \infty$. An example of such relationship
is given in \cref{eq:nodesRing}. We will omit the dependence of $n$ on $h$ when
possible.

\textbf{Step 2: Collocation.} 
Impose that \cref{eq:NF} holds at each node (\textit{collocate the equation} at
each $x_i \in \Xi$). This means replacing \cref{eq:NF} by a set of $n$ equations
\begin{equation}\label{eq:NFColl}
  \begin{aligned}
  &
  \begin{aligned}
    \partial_t u_n(x_i,t) =  -u_n(x_i,t) &+ g(x_i,t) \\
                & + \int_{D} w(x_i,y) f(u_n(y,t))d \mu(y),
  \end{aligned}
  && (x_i,t) \in \Xi \times [0,T] \\
  & u_n(x_i,0) = v(x_i) && x_i \in \Xi 
  \end{aligned}
\end{equation}

@@

\textbf{Step 3: Quadrature.} Select a quadrature for the integral, and solve
\begin{equation}\label{eq:NFODEQuad}
  \begin{aligned}
   & \tilde \alpha'(t) = -\tilde \alpha(t) + \tilde K(\tilde \alpha(t)) + \gamma(t) \qquad  t \in [0,T],\\ 
   & \tilde \alpha (0) = \nu,
  \end{aligned}
\end{equation}  
where $\tilde \alpha(t)$, $\gamma(t), \tilde K(\tilde \alpha(t)), \nu \in \RSet^n$ with
$\gamma_i(t) = g(x_i,t)$, $\nu_i = v(x_i)$, and where $(\tilde \alpha(t))_i$
approximates $u_n(x_i,t)$. The nonlinear mapping $K(\tilde \alpha)$ involves a matrix-vector
multiplication, and incorporates quadrature weights.

\section{Collocation schemes as interpolatory projection schemes}\label{sec:projectionSchemes}

Once we have refined the steps of a collocation scheme, we can bring interpolation
into the picture. In \cite{Avitabile:2023ab} it is shown that convergence estimates
for the collocation scheme (and other schemes) are possible disregarding step 3. In
fact, with just steps 1-2 can estimate how fast $u_n$ tends to $u$, as $n \to \infty$.
Once a convergence rate is established, then this instructs which quadrature scheme
to select: the quadrature should respects this rate, so that we can use $(\tilde
\alpha(t))_i$ as an approximation to $u(x_i,t)$, not simply $u_n(x_i,t)$.

We do not have to get into the details of
\cite{Avitabile:2023ab}, but one aspect is important for these
notes: it is useful to understand how \cref{eq:NFColl} is derived from \cref{eq:NF}
using a projection. The RBFs will provide, in fact, a flexible and accurate
\textit{interpolatory projector}.

To make progress on this, let us assume we seek for a solution to the neural field
equations in the space of continuous functions $\XSet = C(D)$. A projector $P_n$ is a
linear mapping from $\XSet$ to an $n$-dimensional subspace $\XSet_n \subset \XSet$
such that $P_n (P_n v) = P_n v$ for all $v \in \XSet$. The distinctive feature of an
\textit{interpolatory projector} is that it has the property  
\[
  (P_n v)(x_i) = v(x_i), \qquad x_i \in \Xi,
\] 
that is, $P_n v$ is a function of $x$, which approximates $v(x)$, and it is exact
at the nodes $x_i$. The previous sections contain two interpolatory projectors in
disguise. In \cref{eq:LagrangeInterp} we wrote
\[
  v_n(x) = \sum_{j=1}^{n} v(x_j) \ell_j(x). 
\]
Since $v$ is a continuous function, then so $v \in \XSet$, and $v_n$ is a linear combination
of $\{ \ell_j \}_{j=1}^n$, so $v_n \in \XSet_n = \spn \{ \ell_1, \ldots, \ell_n \}$.
This means we can interpret the previous writing as
\[
  (P_n v)(x) = \sum_{j=1}^{n} v(x_j) \ell_j(x),
\]
that is, $v_n$ is the action of $P_n$ on the function $v$, $v_n = P_n v$.
The same can be said about \cref{eq:RBFInterpolation}, which defines another choice
of the interpolant, and another choice of projector $P_n$. A fundamental property of
interpolatory projectors is the following (see \cite[Proposition
4.1]{Avitabile:2023ab}): \da[]{Cite Atkinson and others} for any
$r \in \XSet$, 
\begin{equation}\label{eq:projCollProperty}
P_n r = 0, 
\qquad \text{if, and only if,} \qquad 
(P_n r)(x_i) = 0, \qquad i \in \NSet_n.
\end{equation}
This property is useful in describing the system in terms of residual, as we shall do
in a moment.

We now revisit the neural field equation and the collocation scheme in terms of the
projector $P_n$. Firstly, we rewrite the neural field equation \cref{eq:NF} in
operator form, as the following Cauchy problem on the Banach space $\XSet$
\begin{equation}\label{eq:cauchy}
  \begin{aligned}
  & U'(t) = - U(t) + WF(U(t)) + G(t) =:  N(t,U(t)), \qquad t \in J, \\
  & U(0) = V.
  \end{aligned}
\end{equation}
The identification with \cref{eq:NF} is established by setting $J = [0,T]$,
$V = v(\blank)$, and
\[  
  \begin{aligned}
   & U \colon J \to \XSet, && t \mapsto u(\blank,t),
   & G \colon J \to \XSet, && t \mapsto g(\blank,t), \\
   & W \colon \XSet \to \XSet, && v \mapsto \int_{D} w(\blank,y) v(y) \,d \mu(y),
   & F \colon \XSet \to \XSet, && v \mapsto f(v). 
  \end{aligned}
\]
Under suitable generic assumptions \da[]{if needed, include them}, the Cauchy problem
is well-posed under general assumptions that is, there is a unique $u \in
C^1(J,\XSet)$ satisfying \cref{eq:cauchy}, see
\cite{Potthast:2009bd,Faugeras:2009gn}, and \cite[Lemma 2.7]{Avitabile:2023ab}.

Secondly, it is possible to interpret \cref{eq:NFColl} in operator form, as
\begin{equation}\label{eq:cauchyPn}
  \begin{aligned}
  & \dot U_n(t) = - U_n(t) + P_n WF(U_n(t)) + P_n G(t) =  P_n N(t,U_n(t)), \qquad t \in J, \\
  & U_n(0) = P_n V,
  \end{aligned}
\end{equation}
which is a Cauchy problem on the space $\XSet_{n}$. This problem is also well-posed
and gives a solution $u_n \in C^1(J,\XSet_n)$ and
\cite[Theorem 3.1]{Avitabile:2023ab}.

Using \cref{eq:projCollProperty}, we can now pass from \cref{eq:cauchyPn} to an
equivalent ODE in $\RSet^n$. We define the residual
\[
  R \colon C^1(J,\XSet) \to C(J,\XSet), \qquad U \mapsto U' - N(\blank, U),
\]
rewrite \cref{eq:cauchyPn} as
\[
  P_n \bigl( R(U_n)(t) \bigr) = 0, \qquad t \in J, \qquad 
  P_n \bigl( U_n(0) - V\bigr) = 0, 
\]
which, by property \cref{eq:projCollProperty} is equivalent to
\[
  \begin{aligned}
  & U'_n(t)(x_i) = \bigl[P_n N(t,U_n(t))\bigr](x_i), \qquad (i,t) \in \NSet_n \times J, \\
  & U_n(0)(x_i) = (P_n V)(x_i).
  \end{aligned}
\]
Finally, since $U_n(t) \in \XSet_n$, we can write $U_n(t) = \sum_{j \in \NSet_n}
\alpha_j(t) \ell_j$ and obtain the sought ODE on $\RSet^n$,
\begin{equation} \label{eq:NFODE}
  \begin{aligned}
   & \alpha'(t) = -\alpha(t) + K(\alpha(t)) + \gamma(t) \qquad  t \in [0,T],\\ 
   & \alpha (0) = \nu,
  \end{aligned}
\end{equation}  
where 
\[
  \begin{aligned}
  & \alpha_i(t) = U_n(t)(x_i), && \nu_i = v(x_i),  \\
  & \gamma_i(t) = g(x_i,t),
  && K_i(\alpha) = 
    \int_{D}w(x_i,y) f\Bigl( \sum_{j \in \NSet_n} \alpha_j \ell_j(y)\Bigr) \, d\mu(y)
  \end{aligned}
\]
In passing, we note that the system \cref{eq:NFODE} above is related, but not
identical, to \cref{eq:NFODEQuad}. The former is expressed in terms of 
$K \colon \RSet^n \to \RSet^n$, the latter in terms of
$\tilde K \colon \RSet^n \to \RSet^n$, which adopts a quadrature rule to approximate
the integrals in $K$.

@@

\subsection{References} \label{sec:references} For cross-references I use
\texttt{cleveref}: like this
\cref{eq:test}, like this \Cref{eq:test}, or like this \cref{sec:conventions}, or
this \cref{hyp:trivial}, or this \cref{clm:trivial}.
\begin{equation}\label{eq:test}
  x = y
\end{equation}
